---
output: html_document
---
<!--
  %\VignetteEngine{knitr}
%\VignetteIndexEntry{b) Powell Streams data report}
-->

Powell Streams data report
===

```{r, echo=FALSE,result='hide',message=FALSE, warning=FALSE, fig.width=8,fig.height=6.5}
library(powstreams)
library(dplyr)
library(choroplethr)
library(dataRetrieval)
library(choroplethrMaps)
data(state.regions)

sites <- list_sites(with_timeseries = 'doobs')
df <- state.regions[,c(1,3)]
names(df)[2] <- 'value'
df[,2] <- 0
nwis_sites <- mda.streams:::split_site(sites)
site_data <- readNWISsite(nwis_sites)
for (i in 1:length(sites)){
  
  region <- state.regions[as.numeric(site_data$state_cd[i])==state.regions[,3], 1]
  u.i = df[,1] == region
  if (sum(u.i) == 1){
    df[u.i, 2]<- df[u.i, 2]+1
  }
}

sites_w_either <- unique(c(list_sites(with_timeseries = c('doobs','wtr','disch')), list_sites(with_timeseries = c('doobs','wtr','stage'))))

state_choropleth(df)
```

## sites with DO data: `r length(list_sites(with_timeseries = 'doobs'))` 

## sites with DO, temp, and discharge data: `r length(list_sites(with_timeseries = c('doobs','wtr','disch')))` 

## sites with DO, temp, discharge AND/OR stage: `r length(sites_w_either)`  

## sites with DO and nitrate: `r length(list_sites(with_timeseries = c('doobs','nitrate')))`


## Range of DO for sites with DO and temperature:
<object data="../demo/powstreams_amps.svg" type="image/svg+xml" />

### is those real data?
```{r}
library(powstreams)
site <- 'nwis_08446500'
doobs <- load_timeseries(site, 'doobs')
aug_do <- filter(doobs, months(DateTime)=="August" & strftime(DateTime,'%Y') == '2012')
```

```{r, fig.width=7,fig.height=5}
plot(aug_do, ylab = 'DO (mg/L)')
```

### A closer look

```{r, fig.width=7,fig.height=5}
plot(aug_do[400:750, ], type = 'o', ylab = 'DO (mg/L)', pch = 21, bg='white')
```